\documentclass[twoside,11pt]{article}

\usepackage{aa228-jmlr2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{url}
\usepackage{cleveref}
\usepackage{subcaption}

\begin{document}

% More details can be found here: https://aa228.stanford.edu/final-project/
\title{Final Project Proposal: Cool Project Title}

%===========================================
% Fill in your names and emails
%===========================================
\name{First Last}
\email{email@stanford.edu}

\name{Author Two}
\email{two@stanford.edu}

\maketitle

\section{Goal}
Describe the problem you want to solve, your project goals, and what success looks like. Explain why this problem is interesting. Please cite any sources you think might help in our understanding of the problem \citep{Kochenderfer2022}. (1-2 paragraphs)


\section{Decision Making}
Describe your \textit{sequential} decision making problem. Explain your environment and how decision making affects it. Ensure your problem is truly sequential and not a one-shot decision. Consider sketching the problem as a (PO)MDP, including States, Actions, Transitions, Rewards, and [Observations]. (1-2 paragraphs)

\section{Sources of Uncertainty}
Identify and describe the sources of uncertainty in your problem. Propose how you might model these sources. (1-2 paragraphs)

\section{Sketches of Solution (Optional)}
If you have ideas, propose a sketch of a solution to your problem. This is optional but encouraged, as it will allow for more specific feedback. (1-2 paragraphs if included)

% References
\bibliography{references}


\end{document}

